TrueSkill Through Time: the \proglang{Python} Package

### 2020-08-10 article.tex
TTT: corrijo (parte) de full trueskill

\subsection{Full TrueSkill}

\begin{center}
\tikz{ %
        \node[factor, xshift=-4cm] (fta) {} ;
        \node[const, right=of fta] (nfta) {$f_{t_0}$}; %
        \node[latent, below=of fta,yshift=-0.5cm] (ta) {$t_0$} ; %

@@

        \node[factor, xshift=4cm] (ftc) {} ;
        \node[const, right=of ftc] (nftc) {$f_{t_2}$}; %
        \node[latent, below=of ftc,yshift=-0.5cm] (tc) {$t_2$} ; %

        \node[factor, below=of tb, xshift=-2cm] (fd1) {} ;
        \node[const, left=of fd1] (nfd1) {$f_{d_0}$}; %
        \node[latent, below=of fd1,yshift=-0.5cm] (d1) {$d_{0}$} ; %
        \node[factor, below=of d1,yshift=-0.5cm] (fr1) {} ;

        \node[factor, below=of tb, xshift=2cm] (fd2) {} ;
        \node[const, above=of fd2] (nfd2) {$f_{d_{1}}$}; %
        \node[latent, below=of fd2,yshift=-0.5cm] (d2) {$d_{1}$} ; %
        \node[factor, below=of d2,yshift=-0.5cm] (fr2) {} ;

@@

        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \ \ \ \textbf{3:} \emph{looseLikelihood}$(t_1)$} (tb);

        \path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend left,draw=black!50] node[midway,below,color=black!75] {\scriptsize \textbf{6:} \emph{winLikelihood}$(t_1)$} (tb);

        \path[draw, -latex, fill=black!50,sloped] (ftb) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{prior}$(t_1)$} (tb);

        \path[draw, -latex, fill=black!50,sloped] (fr1) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \textbf{2:} \emph{likelihood}$(d_{0})$} (d1);
        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \textbf{1:} \emph{prior}$(d_{0})$} (d1);

        \path[draw, -latex, fill=black!50,sloped] (fr2) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \textbf{5:} \emph{likelihood}$(d_{0})$} (d2);
        \path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \textbf{4:} \emph{prior}$(d_{0})$} (d2);

@@

@@

\begin{equation}
 \begin{split}
  \emph{prior}(d_{i}) = \iint \mathbb{I}(d_{i} = t_i - t_{i+1} ) \cdot \emph{prior}(t_i) \cdot \emph{prior}(t_{i+1}) \cdot \emph{winLikelihood}(t_{i+1}) \, dt_idt_{i+1}
 \end{split}
\end{equation}

@@

\paragraph{\emph{looseLikelihood}$\bm{(t_{i+1})}$:}

\begin{equation}
 \begin{split}
  \emph{looseLikelihood}(t_{i+1}) = \int \mathbb{I}(d_i>0) \emph{prior}(t_i) \widehat{\emph{likelihood}}(d_i)
 \end{split}
\end{equation}

\paragraph{\emph{winLikelihood}$\bm{(t_{i})}$:}
\begin{equation}
 \begin{split}
  \emph{winLikelihood}(t_{i}) = \int \mathbb{I}(d_i>0) \emph{prior}(t_{i+1}) \widehat{\emph{likelihood}}(d_i)
 \end{split}
\end{equation}

>>>>

\section{Full TrueSkill}

\begin{center}
\tikz{ %        
        \node[factor, xshift=-5cm] (fta) {} ;
        \node[const, right=of fta] (nfta) {$f_{t_0}$}; %
        \node[latent, below=of fta,yshift=-0.5cm] (ta) {$t_0$} ; %

@@

        \node[factor, xshift=5cm] (ftc) {} ;
        \node[const, right=of ftc] (nftc) {$f_{t_2}$}; %        
        \node[latent, below=of ftc,yshift=-0.5cm] (tc) {$t_2$} ; %

        \node[factor, below=of tb, xshift=-3cm] (fd1) {} ;
        \node[const, left=of fd1] (nfd1) {$f_{d_0}$}; %        
        \node[latent, below=of fd1,yshift=-1cm] (d1) {$d_{0}$} ; %
        \node[factor, below=of d1,yshift=-1cm] (fr1) {} ;

        \node[factor, below=of tb, xshift=3cm] (fd2) {} ;
        \node[const, above=of fd2] (nfd2) {$f_{d_{1}}$}; %        
        \node[latent, below=of fd2,yshift=-1cm] (d2) {$d_{1}$} ; %
        \node[factor, below=of d2,yshift=-1cm] (fr2) {} ;

@@

        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize  \emph{loseLikelihood}$(t_1)$} (tb);

        \path[draw, -latex, fill=black!50,sloped] (tb) edge[bend left,draw=black!50] node[midway,below,color=black!75] {\scriptsize  \emph{losePosterior}$(t_1)$} (fd1);

        \path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend right,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{winLikelihood}$(t_1)$} (tb);

        \path[draw, -latex, fill=black!50,sloped] (tb) edge[bend right,draw=black!50] node[midway,below,color=black!75] {\scriptsize \emph{winPosterior}$(t_1)$} (fd2);

        \path[draw, -latex, fill=black!50,sloped] (fta) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{prior}$(t_0)$} (ta);

        \path[draw, -latex, fill=black!50,sloped] (fr1) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \emph{likelihood}$(d_{0})$} (d1);

        \path[draw, -latex, fill=black!50,sloped] (d1) edge[bend right,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{\ \ posterior}$(d_{0})$} (fd1);

        \path[draw, -latex, fill=black!50,sloped] (fd1) edge[bend right,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{prior}$(d_{0})$} (d1);

        \path[draw, -latex, fill=black!50,sloped] (tc) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \emph{posterior}$(t_0)$} (ftc);

        %\path[draw, -latex, fill=black!50,sloped] (fr2) edge[bend left,draw=black!50] node[midway,above,color=black!75, rotate=180] {\scriptsize \textbf{5:} \emph{likelihood}$(d_{0})$} (d2);

        %\path[draw, -latex, fill=black!50,sloped] (fd2) edge[bend left,draw=black!50] node[midway,above,color=black!75] {\scriptsize \textbf{4:} \emph{prior}$(d_{0})$} (d2);

@@

\paragraph{$\bm{\emph{winPosterior}(t_i)}$:}

\begin{equation}
 \begin{split}
  \emph{winPosterior}(t_{i}) = \emph{prior}(t_i) \cdot \emph{winLikelihood}(t_i)
 \end{split}
\end{equation}

\paragraph{$\bm{\emph{losePosterior}(t_i)}$:}

\begin{equation}
 \begin{split}
  \emph{losePosterior}(t_{i}) = \emph{prior}(t_i) \cdot \emph{loseLikelihood}(t_i)
 \end{split}
\end{equation}

@@

\begin{equation}
 \begin{split}
  \emph{prior}(d_{i}) = \iint \mathbb{I}(d_{i} = t_i - t_{i+1} ) \cdot winPosterior(t_i) \cdot losePosterior(t_{i+1}) \, dt_idt_{i+1} 
 \end{split}
\end{equation}

@@

\paragraph{$\bm{\widehat{\emph{posterior}}(d_i)}$:}

\begin{equation}
\begin{split}
\widehat{\emph{posterior}}(d_i) &= \widehat{\emph{likelihood}}(d_i)
\end{split}
\end{equation}

\paragraph{\emph{loseLikelihood}$\bm(t_{i+1})$:}

\begin{equation}
 \begin{split}
  \emph{loseLikelihood}(t_{i+1}) = \iint \mathbb{I}(d_{i} = t_i - t_{i+1} ) \emph{winPosterior}(t_i) \widehat{\emph{posterior}}(d_i) \, dd_idt_{i+1} 
 \end{split}
\end{equation}

\paragraph{\emph{winLikelihood}$\bm(t_{i})$:}

\begin{equation}
 \begin{split}
  \emph{winLikelihood}(t_{i}) = \iint \mathbb{I}(d_{i} = t_i - t_{i+1} ) \emph{losePosterior}(t_{i+1}) \widehat{\emph{posterior}}(d_i) \, dd_idt_{i+1} 
 \end{split}
\end{equation}
